---
title: "Round 1 - Gear analysis"
author: "Arlie McCarthy and Josh Brian"
date: "`r Sys.Date()`"
output: github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "workflow") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
library(missMDA)
library(tidyverse)
library(here)
library(readxl)
library(ggh4x)
library(cowplot)
```

## Load data

```{r load data}
surveydata <- read_excel(here::here("data", "R1_gear_results.xlsx"), sheet = "Sheet1")
gear_groups <- read_excel(here::here("data", "2021_04_fishing_gear_matrix_REV.xlsx"), sheet = "gear_categories")
```

## Generate figures showing 
General figure for the manuscript showing the groups of gear types and the classifications from survey respondents. Groups are based on larger categories. 

```{r re-shape for plotting}
long_data <- pivot_longer(surveydata %>% select("name", "Purse seines":"Blast/explosives/dynamite"), cols = "Purse seines":"Blast/explosives/dynamite", values_to = "response", names_to = "Gear", names_repair = "check_unique") %>% 
  join(gear_groups) %>% 
  drop_na() %>% 
  dplyr::group_by(Gear) %>% 
  dplyr::mutate(gear_median = median(response)) %>% 
  dplyr::group_by(Category) %>% 
  dplyr::mutate(cat_median = median(response))

cat_levels <- long_data %>% 
  dplyr::group_by(Category) %>% 
  dplyr::summarise(mean(cat_median))
cat_levels

long_data$Category <- factor(long_data$Category, levels = c("Chemical and Blast", "Dredges", "Gillnets and entangling nets", "Trawls", "Seine nets", "Surrounding nets", "Falling gear", "Hooks and lines", "Lift nets", "Traps", "Miscellaneous"))
```
Now that the data is in the correct format, we can visualise it as a violin plot.

```{r gear plot}
gear_plot <- ggplot(long_data, aes(x = short_name, y = response, fill = gear_median)) + 
  geom_violin(alpha = 0.7, colour = "darkgrey") +
  stat_summary(fun = "median", colour = "black", size = 2, geom = "point") +
  scale_fill_viridis_c(name = "Median response", alpha = 0.7) +
  scale_color_viridis_c() +
  facet_wrap(~Category, scales = "free_x", shrink = FALSE) +
  theme_cowplot() +
  scale_x_discrete(expand = expansion(add = 1)) +
  theme(axis.text.x = element_text(size = 7, angle = 30),
        legend.position = c(0.78, 0.15),
        axis.text.y = element_text(size = 7),
        strip.text.y = element_text(size = 9,
                                    angle = 0),
        axis.title = element_text(size = 9),
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 7),
        strip.text = element_text(size = 9))+
  labs(x = "Fishing gear or practice", y = "Potential destructiveness")
gear_plot
```
save the plot

```{r save gear plot}
save_plot(here::here("figures", "gear_plot.png"), gear_plot, base_width = 180, base_height = 125, units = "mm")
```

Create table showing the summary statistics for each gear.

```{r summary stats}
summary_data <- long_data %>% 
  drop_na() %>% 
  dplyr::group_by(Category, Gear) %>% 
  dplyr::summarise(count = length(response),
            mean = mean(response), 
            stdev = sd(response),
            median = median(response)) %>% 
  dplyr::select(Category, Gear, median, everything())
summary_data
```

# Run Principal Components Analysis

We first run a standard PCA analysis. 

```{r pca1}
#gearpca <- prcomp(surveydata[ ,c(8:55)], center=TRUE, scale. = TRUE)
```

Note that this doesn't work because there are missing values. To correct for this we need to impute data. We ese imputePCA function from missMDA package as it is the best and most defendable method 
(see Dray, S., & Josse, J. (2015). Principal component analysis with missing values:a comparative survey of methods. Plant Ecology, 216(5), 657-667.)

```{r impute data}
#just select the columns of interest
datatoimpute <- select(surveydata, "Purse seines":"Blast/explosives/dynamite")

#impute the missing values 

imputeddata <- imputePCA(datatoimpute, ncp=2)
imputedmatrix <- as.data.frame(imputeddata$completeObs)

#Extract possible correlating variables

variables <- select(surveydata, homecontinent:oceanregion)

#combine the variables and imputed data

pcadata <- bind_cols(variables, imputedmatrix)
```

Now we can actually run the PCA

```{r pca2}
gearpca <- prcomp(pcadata[ ,c(7:54)], center=TRUE, scale. = TRUE)
summary(gearpca)
```

## Visualise the PCA
Now the we have the PCA we can plot it. Here we use a range of groupings (based on demographic data of respondents). 

```{r}
#Show just dots (individuals)
ggbiplot(gearpca, var.axes=FALSE) + theme_classic() 

#Show with gears overlaid
ggbiplot(gearpca) + theme_classic() 

#Look at comparison with sector
ggbiplot(gearpca, ellipse=TRUE, groups=pcadata$sector, var.axes=FALSE) + theme_classic() 

#Look at comparison with ocean region
ggbiplot(gearpca, ellipse=TRUE, groups=pcadata$oceanregion, var.axes=FALSE) + theme_classic() 

#Look at comparison with home continent
ggbiplot(gearpca, ellipse=TRUE, groups=pcadata$homecontinent, var.axes=FALSE) + theme_classic() 

#Look at comparison with whether their home and work continents are the same
ggbiplot(gearpca, ellipse=TRUE, groups=pcadata$homeworkdiff, var.axes=FALSE) + theme_classic() 
```

## Save plots

Finally, we save the sector plot for use in the manuscript (supplementary information).
```{r}
r1_sector_pca <- ggbiplot(gearpca, ellipse=TRUE, groups=pcadata$sector, var.axes=FALSE) +
geom_point(aes(colour = pcadata$sector)) +
scale_color_brewer(type = "qual", palette = "Dark2") + 
  theme_classic()
r1_sector_pca
ggsave2(here::here("figures", "r1_sector_pca.jpg"),
  plot = r1_sector_pca,
  device = "jpg",
  width = 20,
  height = 10,
  units = "cm")
```