---
title: "Survey_R2andR3_likert_analysis"
author: "Arlie McCarthy"
date: "`r Sys.Date()`"
output: github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "workflow") })
---

This file generates the figures of responses to statements in R2 and R3.

# Set-up

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(janitor)
library(here)
library(readxl)
library(reshape2)
library(RColorBrewer)
library(dplyr)
library(ggthemes)
library(stringr)
library(ggbiplot)
library(sf)
library(rnaturalearth)
library(cowplot)
library(agrmt)
library(ggh4x)
library(kableExtra)
```

# Importing Data

The first step is to import data for both round 2 and round 3, then join them into a file that allows them to be plotted together

```{r import R2 data}
r2_likert_responses <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "responses_wider")
r2_responses_longer <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "responses")
r2_likert_questions <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "questions")
tabr2 <- r2_likert_responses %>% 
  filter(Name != "Lang",
         Name != "Country_from",
         Name != "Country_predominantely_work",
         Name != "Ocean_basin",
         Name != "Years_experience",
         Name != "Fishing_gear_exp",
         Name != "email",
         Name != "sector") %>% 
  mutate(q_number = Name) %>% 
  left_join(r2_likert_questions, by = "q_number") %>% 
  select(-Name) %>% 
  pivot_longer(names_to = "name", values_to = "response", cols = 1:54) %>% 
  select(question, name, response) %>% 
  group_by(question, response) %>% 
  dplyr::summarise(pcent = n()/54) %>% 
  pivot_wider(names_from = response, values_from = pcent) %>% 
  select("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree",  "Strongly agree") %>% 
  replace_na(list("Strongly disagree" = 0,
                  "Somewhat disagree" = 0,
                  "Neither agree nor disagree" = 0,
                  "Somewhat agree" = 0,
                  "Strongly agree" = 0)) %>% 
               left_join(r2_likert_questions)
mylevelsr2<-c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree",  "Strongly agree")

round3_question_key <- read_excel(here::here("data/round3_question_key.xlsx"))
round3_question_key$question<-str_wrap(round3_question_key$question, width = 50)
```


```{r import R3 data}
r3_likert_responses <- read_excel(here::here("data/Rd3_Results_Final.xlsx"), sheet = "responses_wider")
r3_responses_longer <- read_excel(here::here("data/Rd3_Results_Final.xlsx"), sheet = "responses")
r3_likert_questions <- read_excel(here::here("data/Rd3_Results_Final.xlsx"), sheet = "questions")
r3_likert_questions <- r3_likert_questions %>% 
  mutate(question_with_number = paste(q_number_rd3, question))

tabr3 <- r3_likert_responses %>% 
  filter(Name != "Lang",
         Name != "email",
         Name != "sector") %>% 
  mutate(q_number_rd3 = Name) %>% 
  left_join(r3_likert_questions, by = "q_number_rd3") %>% 
  select(-Name) %>% 
  pivot_longer(names_to = "name", values_to = "response", cols = 1:39) %>% 
  select(question_with_number, name, response) %>% 
  group_by(question_with_number, response) %>% 
  dplyr::summarise(pcent = n()/39) %>% 
  pivot_wider(names_from = response, values_from = pcent) %>% 
  select("Strongly disagree", "Somewhat disagree", "Prefer not to say", "Somewhat agree",  "Strongly agree") %>% 
  replace_na(list("Strongly disagree" = 0,
                  "Somewhat disagree" = 0,
                  "Prefer not to say" = 0,
                  "Somewhat agree" = 0,
                  "Strongly agree" = 0)) %>% 
               left_join(r3_likert_questions)
mylevelsr3<-c("Strongly agree","Somewhat agree", "Somewhat disagree", "Strongly disagree", "Prefer not to say")
mybreaks <- c("#0571B0", "#92C5DE", "#F4A582", "#CA0020", "#ffffff")

tabr3$agree = tabr3$`Strongly agree` + tabr3$`Somewhat agree`
tabr3$disagree = tabr3$`Strongly disagree` + tabr3$`Somewhat disagree`
tabr3$sum_pcent = tabr3$`Strongly agree` + tabr3$`Somewhat agree` + tabr3$`Strongly disagree` + tabr3$`Somewhat disagree`
#tabr3$question = paste( "* ", tabr3$question)
# this line removed to remove the asterisk in the final figures
```


Now join the two dataframes to replace the questions asked in R2 with those asked in R3 BUT also add a variable that indicates which round the answer is from so that it can be displayed in the figure, too. 

For these figures a version with an asterisk to indicate which questions were asked in round 3, and a version to indicate which questions were only asked in round 2. The version with the asterisk is saved with * at the end of the filename and is included in the supplementary informtion. The version without the asterisk is used in the main manuscript. To avoid duplicating almost identical sections of code, the version without the asterisk is shown below.

```{r join dataframes}
`%!in%` = Negate(`%in%`)
tabr2$round = 2
tabr3$round = 3
tabr3.v2 <- tabr3 %>% 
  ungroup() %>% 
  select("question",
         "Strongly disagree",
         "Somewhat disagree",
         "Prefer not to say", 
         "Somewhat agree", 
         "Strongly agree",
         "q_number",
         "q_group",
         "q_start_phrase",
         "broad_category",
         "theme",
         "narrow_theme",
         "short_question",
         "round"
         )

tab <- tabr2 %>% 
  filter(q_number %!in% tabr3.v2$q_number) %>% 
  full_join(tabr3.v2)
tab$question <- str_wrap(tab$question, width = 55)
tab$narrow_theme <- str_wrap(tab$narrow_theme, width = 12)

tab2<- tab %>% 
  dplyr::select(question,
                `Strongly disagree`,
                `Somewhat disagree`,
                `Somewhat agree`,
                `Strongly agree`,
                -`Prefer not to say`,
                -`Neither agree nor disagree`,
                q_number:round) %>% 
  pivot_longer(cols = c(2:5))
tab3 <- tab2 %>% 
  mutate(col = case_when(name == "Strongly disagree" ~ "#CA0020",
                         name == "Somewhat disagree" ~ "#F4A582",
                         name == "Somewhat agree" ~ "#92C5DE",
                         name == "Strongly agree" ~ "#0571B0"))
tab3$value<-tab3$value*100
```

Create the high and low values to make the plot
```{r data prep for plotting}
highs_impacts<-tab3 %>% dplyr::filter(broad_category == "Impacts",
                               name == "Somewhat agree" |
                                 name == "Strongly agree" |
                                 name == "midhigh") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
highs_chars<-tab3 %>% dplyr::filter(broad_category == "Characteristics",
                               name == "Somewhat agree" |
                                 name == "Strongly agree" |
                                 name == "midhigh")  %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
lows_impacts<-tab3 %>% dplyr::filter(broad_category == "Impacts",
                               name == "Somewhat disagree" |
                                 name == "Strongly disagree" |
                                 name == "midlow") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(theme, narrow_theme)
lows_chars<-tab3 %>% dplyr::filter(broad_category == "Characteristics",
                               name == "Somewhat disagree" |
                                 name == "Strongly disagree" |
                                 name == "midlow") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
highs_chars_concept = highs_chars %>% filter(theme == "Concept")
highs_chars_scope = highs_chars %>% filter(theme == "Scope")
lows_chars_concept = lows_chars %>% filter(theme == "Concept")
lows_chars_scope = lows_chars %>% filter(theme == "Scope")
highs_impacts_eco = highs_impacts %>% filter(theme == "Ecological")
highs_impacts_socio = highs_impacts %>% filter(theme == "Socio-economic")
lows_impacts_eco = lows_impacts %>% filter(theme == "Ecological")
lows_impacts_socio = lows_impacts %>% filter(theme == "Socio-economic")
```

# Figures grouped by broad category

```{r concept figure}
chars_concept_fig <- ggplot() + geom_bar(data=highs_chars_concept, aes(x = reorder(question, value), y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_chars_concept, aes(x = question, y=-value, fill=col), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  geom_hline(yintercept = -70, color =c("black")) +
  geom_hline(yintercept = 70, color =c("black")) +
  scale_fill_identity("Response types:", labels = mylevelsr3, breaks = mybreaks, guide="legend") +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 10)) + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8,
                                   hjust = 1,
                                   angle = 45),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = c(0.95, -0.1),
        legend.direction = "horizontal",
        legend.justification="right",
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 8))

chars_concept_fig
```

``` {r save concept figure}
ggsave2(filename = here::here("figures", "concept_figure.png"),
  plot = chars_concept_fig,
  device = "png",
  width = 183,
  height = 123,
  units = "mm"
)
```

###And now the plot for the scope data

```{r scope figure}
chars_scope_fig <- ggplot() + geom_bar(data=highs_chars_scope,  aes(x = reorder(question, value), y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_chars_scope, aes(x = question, y=-value, fill=col), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  geom_hline(yintercept = -70, color =c("black")) +
  geom_hline(yintercept = 70, color =c("black")) +
#  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Response types:", labels = mylevelsr3, breaks = mybreaks, guide="legend") +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 10)) + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8,
                                   hjust = 1,
                                   angle = 45),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = c(0.95, -0.08),
        legend.direction = "horizontal",
        legend.justification="right",
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 8))
chars_scope_fig
```


``` {r save scope figure}
ggsave2(filename = here::here("figures", "scope_figure.png"),
  plot = chars_scope_fig,
  device = "png",
  width = 183,
  height = 163,
  units = "mm"
)
```

Same again but for the impacts data

```{r}
impacts_eco_fig <- ggplot() + geom_bar(data=highs_impacts_eco, aes(x = reorder(question, value), y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_impacts_eco, aes(x = question, y=-value, fill=col), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  geom_hline(yintercept = -70, color =c("black")) +
  geom_hline(yintercept = 70, color =c("black")) +
#  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Response types:", labels = mylevelsr3, breaks = mybreaks, guide="legend") +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 10)) + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8,
                                   hjust = 1,
                                   angle = 45),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = c(0.95, -0.15),
        legend.direction = "horizontal",
        legend.justification="right",
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 8))
#  theme(legend.position = "none")
impacts_eco_fig
```

``` {r save eco impacts figure}
ggsave2(filename = here::here("figures", "eco_impacts_figure.png"),
  plot = impacts_eco_fig,
  device = "png",
  width = 183,
  height = 103,
  units = "mm"
)
```

```{r}
#And now the plot for the socio-economic impacts data
impacts_socio_fig <- ggplot() + geom_bar(data=highs_impacts_socio, aes(x = reorder(question, value), y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_impacts_socio, aes(x = question, y=-value, fill=col), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  geom_hline(yintercept = -70, color =c("black")) +
  geom_hline(yintercept = 70, color =c("black")) +
#  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Response types:", labels = mylevelsr3, breaks = mybreaks, guide="legend") +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 10)) + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8,
                                   hjust = 1,
                                   angle = 45),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = c(0.95, -0.15),
        legend.direction = "horizontal",
        legend.justification="right",
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 8))
impacts_socio_fig

```

Save the plot
``` {r save socio impacts figure}
ggsave2(filename = here::here("figures", "socio_impacts_figure.png"),
  plot = impacts_socio_fig,
  device = "png",
  width = 183,
  height = 83,
  units = "mm"
)
```

The impacts figures are both relatively small so can be combined into one figure

```{r combine impacts figures}
impacts_legend_row <- plot_grid(get_legend(impacts_eco_fig + theme(
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8))),
  nrow = 1)
impacts_fig <- plot_grid(impacts_eco_fig + theme(legend.position = "none"), impacts_socio_fig, align = "v", ncol = 1, rel_heights = c(1, 0.8), labels = c("a) Ecological impact statements", "b) Socio-economic impact statements"), label_size = 9, vjust = 1, hjust = 0)
impacts_fig
impacts_fig_both <- plot_grid(impacts_fig,
                            impacts_legend_row,
                            ncol = 1, nrow = 2,
                            rel_heights = c(1, 0.04))
impacts_fig_both
save_plot(here::here("figures", "impacts_fig_both.png"), impacts_fig_both, base_width = 183, base_height = 168, units = "mm")
```

