---
title: "Survey Rd 2 analysis"
author: "Arlie McCarthy"
date: "`r Sys.Date()`"
output: github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "workflow") })
---
This file contains the scripts for analysing the likert responses to statements in R2, establishing which questions will be asked again in R3, generating individual feedback figures for respondents, and conducting a PCA on responses to statements in R2. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(janitor)
library(here)
library(readxl)
library(reshape2)
library(RColorBrewer)
library(dplyr)
library(ggthemes)
library(stringr)
library(ggbiplot)
library(sf)
library(rnaturalearth)
library(cowplot)
library(agrmt)
library(ggh4x)
```

## Import survey q_numbers and responses


```{r import data}
r2_likert_responses <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "responses_wider")
r2_responses_longer <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "responses")
r2_likert_questions <- read_excel(here::here("data/R2_responses.xlsx"), sheet = "questions")
tab <- r2_likert_responses %>% 
  filter(Name != "Lang",
         Name != "Country_from",
         Name != "Country_predominantely_work",
         Name != "Ocean_basin",
         Name != "Years_experience",
         Name != "Fishing_gear_exp",
         Name != "email",
         Name != "sector") %>% 
  mutate(q_number = Name) %>% 
  left_join(r2_likert_questions, by = "q_number") %>% 
  select(-Name) %>% 
  pivot_longer(names_to = "name", values_to = "response", cols = 1:54) %>% 
  select(question, name, response) %>% 
  group_by(question, response) %>% 
  dplyr::summarise(pcent = n()/54) %>% 
  pivot_wider(names_from = response, values_from = pcent) %>% 
  select("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree",  "Strongly agree") %>% 
  replace_na(list("Strongly disagree" = 0,
                  "Somewhat disagree" = 0,
                  "Neither agree nor disagree" = 0,
                  "Somewhat agree" = 0,
                  "Strongly agree" = 0)) %>% 
               left_join(r2_likert_questions)
mylevels<-c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree",  "Strongly agree")

round3_question_key <- read_excel(here::here("data/round3_question_key.xlsx"))
round3_question_key$question<-str_wrap(round3_question_key$question, width = 50)
```

# Prepare response data for plotting

```{r}
tab$question<-str_wrap(tab$question, width = 50)
#numcenter<-ceiling(numlevels/2)+1
tab <- tab %>% mutate(midvalues = `Neither agree nor disagree` / 2)
tab$all_agree <- tab$`Somewhat agree` + tab$`Strongly agree`
tab$all_disagree <- tab$`Strongly disagree` + tab$`Somewhat disagree`
tab$polarisation <- tab$all_agree - tab$all_disagree # scores closer to 0 will be the most polarised
tab2<- tab %>% 
  mutate(midlow = midvalues,
         midhigh = midvalues) %>% 
  dplyr::select(question, `Strongly disagree`, `Somewhat disagree`, midlow, midhigh, `Somewhat agree`, `Strongly agree`, broad_category:short_question)
tab2 <- tab2  %>% arrange(question)
# Write the summary information into excel workbook
#write.xlsx(x = as.data.frame(tab), file = here::here("Survey_Results_Summary.xlsx"),
#      sheetName = "Round_2", append = FALSE, showNA = FALSE)

numlevels<-length(mylevels)+1
point1<-2
point2<-((numlevels)/2)+1
point3<-point2+1
point4<-numlevels+1
mymin<-(ceiling(max(rowSums(tab2[,point1:point2]))*4)/4)*-100
mymax<-(ceiling(max(rowSums(tab2[,point3:point4]))*4)/4)*100

temp.rows<-nrow(tab2)
pal<-brewer.pal((numlevels-1),"RdBu")
pal[ceiling(numlevels/2)]<-"#DFDFDF"
legend.pal<-pal
pal<-c(pal[1:(ceiling(numlevels/2)-1)], pal[ceiling(numlevels/2)], 
       pal[ceiling(numlevels/2)], pal[(ceiling(numlevels/2)+1):(numlevels-1)])

tab3<-tab2 %>% 
  pivot_longer(cols = c(2:7)) %>%
  arrange(question)
tab3 <- tab3 %>% 
  mutate(col = case_when(name == "Strongly disagree" ~ "#CA0020",
                         name == "Somewhat disagree" ~ "#F4A582",
                         name == "midlow" ~ "#DFDFDF",
                         name == "midhigh" ~ "#DFDFDF",
                         name == "Somewhat agree" ~ "#92C5DE",
                         name == "Strongly agree" ~ "#0571B0"))
tab3$value<-tab3$value*100
#tab3$question<-factor(tab3$question, levels = tab2$question[order(-(tab2[,2]+tab2[,3]+tab2[,4]))])
tab3 <- tab3 %>% group_by(broad_category, theme, narrow_theme, short_question)

highs_impacts<-tab3 %>% dplyr::filter(broad_category == "Impacts",
                               name == "Somewhat agree" |
                                 name == "Strongly agree" |
                                 name == "midhigh") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
highs_chars<-tab3 %>% dplyr::filter(broad_category == "Characteristics",
                               name == "Somewhat agree" |
                                 name == "Strongly agree" |
                                 name == "midhigh")  %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
lows_impacts<-tab3 %>% dplyr::filter(broad_category == "Impacts",
                               name == "Somewhat disagree" |
                                 name == "Strongly disagree" |
                                 name == "midlow") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(theme, narrow_theme)
lows_chars<-tab3 %>% dplyr::filter(broad_category == "Characteristics",
                               name == "Somewhat disagree" |
                                 name == "Strongly disagree" |
                                 name == "midlow") %>% 
  arrange(theme, narrow_theme, short_question) %>% 
  group_by(narrow_theme)
highs_chars_concept = highs_chars %>% filter(theme == "Concept")
highs_chars_scope = highs_chars %>% filter(theme == "Scope")
lows_chars_concept = lows_chars %>% filter(theme == "Concept")
lows_chars_scope = lows_chars %>% filter(theme == "Scope")
highs_impacts_eco = highs_impacts %>% filter(theme == "Ecological")
highs_impacts_socio = highs_impacts %>% filter(theme == "Socio-economic")
lows_impacts_eco = lows_impacts %>% filter(theme == "Ecological")
lows_impacts_socio = lows_impacts %>% filter(theme == "Socio-economic")
```
# Create figures of responses

Concept figure
```{r concept}
chars_concept_fig <- ggplot() + geom_bar(data=highs_chars_concept, aes(x = short_question, y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_chars_concept, aes(x = short_question, y=-value, fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Percent:", labels = mylevels, breaks=legend.pal, guide="legend") + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(
                                   size = 8),
        axis.text.x = element_text(
                                   size = 8),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = "bottom")
  #scale_y_continuous(breaks=seq(mymin,mymax,25), limits=c(mymin,mymax))

chars_concept_fig

ggsave2(filename = here::here("figures", "characteristics_figure.pdf"),
  plot = chars_concept_fig,
  device = "pdf",
  width = 183,
  units = "mm"
)
```

Scope figure
```{r scope figure}
#And now the plot for the scope data
chars_scope_fig <- ggplot() + geom_bar(data=highs_chars_scope, aes(x = short_question, y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_chars_scope, aes(x = short_question, y=-value, fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Percent:", labels = mylevels, breaks=legend.pal, guide="legend") + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = "none")
chars_scope_fig


legend <- get_legend(chars_concept_fig + theme(
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 8)))

legend_row <- plot_grid(get_legend(chars_concept_fig + theme(
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8))),
  nrow = 1)
legend
chars_fig <- plot_grid(chars_concept_fig + theme(legend.position = "none"), chars_scope_fig, align = "v", ncol = 1, rel_heights = c(1, 1.3), labels = c("Concept-related statements", "Scope-related statements"), label_size = 9, vjust = 1)
chars_fig
chars_fig_both <- plot_grid(chars_fig,
                            legend_row,
                            ncol = 1, nrow = 2,
                            rel_heights = c(1, 0.04))
chars_fig_both
save_plot(here::here("figures", "chars_fig_both.pdf"), chars_fig_both, base_width = 183, base_height = 170, units = "mm")
```
Same again but for the impacts data

```{r impacts}
impacts_eco_fig <- ggplot() + geom_bar(data=highs_impacts_eco, aes(x = short_question, y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_impacts_eco, aes(x = short_question, y=-value, fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Percent:", labels = mylevels, breaks=legend.pal, guide="legend") + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(
                                   size = 8),
        axis.text.x = element_text(
                                   size = 8),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = "bottom") +
  scale_y_continuous(breaks=seq(mymin,mymax,25), limits=c(mymin,mymax))

impacts_eco_fig

#And now the plot for the socio-economic data
impacts_socio_fig <- ggplot() + geom_bar(data=highs_impacts_socio, aes(x = short_question, y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_impacts_socio, aes(x = short_question, y=-value, fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  facet_grid(narrow_theme ~ ., scales = "free_y", drop = TRUE, space = "free", shrink = TRUE) +
  scale_fill_identity("Percent:", labels = mylevels, breaks=legend.pal, guide="legend") + 
  theme_cowplot() + 
  coord_flip() +
  labs(y="",x="") +
  theme(axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8),
        strip.text.y = element_text(size = 8,
                                    angle = 0)) +
  theme(legend.position = "none") +
  scale_y_continuous(breaks=seq(mymin,mymax,25), limits=c(mymin,mymax))
impacts_socio_fig

impacts_legend_row <- plot_grid(get_legend(impacts_eco_fig + theme(
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8))),
  nrow = 1)
impacts_fig <- plot_grid(impacts_eco_fig + theme(legend.position = "none"), impacts_socio_fig, align = "v", ncol = 1, rel_heights = c(1, 0.8), labels = c("Ecological impact statements", "Socio-economic impact statements"), label_size = 9, vjust = 1, hjust = 0)
impacts_fig
impacts_fig_both <- plot_grid(impacts_fig,
                            impacts_legend_row,
                            ncol = 1, nrow = 2,
                            rel_heights = c(1, 0.04))
impacts_fig_both
save_plot(here::here("figures", "impacts_fig_both.pdf"), impacts_fig_both, base_width = 183, base_height = 170, units = "mm")
```

# PCAs on demographic data from responses to likert questions

## Run PCA
```{r}
library(hopkins)
library(paran)
library(factoextra)
likert_pca <- prcomp(r2_responses_longer[ ,c(13:57)], center=TRUE, scale. = TRUE)
summary(likert_pca)
paran(r2_responses_longer[ ,c(13:57)], iterations=10000, quietly=FALSE,
    status=FALSE, all=TRUE, cfa=FALSE, graph=TRUE,
    color=TRUE, col=c("black","red","blue"),
    lty=c(1,2,3), lwd=1, legend=TRUE, file="",
    width=640, height=640, grdevice="png", seed=0, mat=NA, n=NA)
#using parallel analysis, only 3 factors should be retained because they have eigenvalues greater than 1, and also 3 have higher eigenvalues than random
eig.val.r2<-get_eigenvalue(likert_pca) #kaiser criterion
eig.val.r2
#suggests 12 dimesions with values over 1, 46% of variance explained by 3 dimensions, 79% by 12 dimensions
results <- likert_pca$x
hopkins(r2_responses_longer[ ,c(13:57)], m=nrow(results)-1) 
clusterabilitytest(r2_responses_longer[ ,c(13:57)], "dip", reduction = "pca")
clusterabilitytest(r2_responses_longer[ ,c(13:57)], "dip", reduction = "distance")
clusterabilitytest(r2_responses_longer[ ,c(13:57)], "silverman", reduction = "pca")
#all four measures of clusterability found no clustering in the data

#Show just dots (individuals)
ggbiplot(likert_pca, var.axes=FALSE) + theme_classic() 

#Show with questions overlaid
ggbiplot(likert_pca) + theme_classic() 

#Look at comparison with sector
pca_sector <- ggbiplot(likert_pca, ellipse=TRUE, groups=r2_responses_longer$sector, var.axes=FALSE) + theme_classic() 
pca_sector
ggsave2(here::here("figures", "PCA_sector.jpg"),
  plot = pca_sector,
  device = "jpg",
  width = 20,
  height = 10,
  units = "cm")

#Look at comparison with ocean region
ggbiplot(likert_pca, ellipse=TRUE, groups=r2_responses_longer$Ocean_basin, var.axes=FALSE) + theme_classic() + theme(legend.position = "none")

#Look at comparison with home continent
ggbiplot(likert_pca, ellipse=TRUE, groups=r2_responses_longer$home_continent, var.axes=FALSE) + theme_classic() 

#Look at comparison with whether their home and work continents are the same
ggbiplot(likert_pca, ellipse=TRUE, groups=r2_responses_longer$homeworkdiff, var.axes=FALSE) + theme_classic() 

#Look at comparison with number of years experience
ggbiplot(likert_pca, ellipse=TRUE, groups=r2_responses_longer$Years_experience, var.axes=FALSE) + theme_classic() 

```

#General information

Round 2 of the survey had 54 responses (51 in English and 3 in Spanish). Respondents were from 25 countries and 6 continents (Europe 56%, Oceania 15%, South America 9%, Asia 7%, North America 7%, Africa 6%). Experts worked across 29 countries and 6 continents (Europe 46%, Asia 17%, Oceania 15%, South America 7%, North America 7%, Africa 7%). Experts had worked in all listed ocean regions (Indian, North and South Pacific, North and South Atlantic, Southern Ocean), with 20 of 54 37% of respondents having worked in multiple regions.  

```{r}
length(unique(r2_responses_longer$Country_from))

r2_responses_longer %>% group_by(home_continent) %>% dplyr::summarise(continent = n()) %>% 
  mutate(continent_pcent = continent/54 * 100)

length(unique(r2_responses_longer$Country_predominantely_work))

r2_responses_longer %>% group_by(work_continent) %>% dplyr::summarise(continent = n()) %>% 
  mutate(continent_pcent = continent/54 * 100)

20/54
```
## Creating demographic maps

Import the country baselayer for mapping.
```{r import world map}
world <- ne_countries(scale = "medium", returnclass = "sf") %>% 
  st_transform(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m no_defs")
```

## Check that the countries given in the survey data align with the countries in the mapping data.

```{r check respondent countries against map data}
country_information <- r2_responses_longer %>% 
  mutate(country_worked = Country_predominantely_work,
         country_from = Country_from,
         country_from_in_map = case_when(country_from %in% world$name_long ~ TRUE, 
                                         TRUE ~ FALSE),
         country_worked_in_map = case_when(country_worked %in% world$name_long ~ TRUE, 
                                         TRUE ~ FALSE)
  )
country_information %>% 
  filter(country_from_in_map == FALSE) %>% 
  group_by(country_from) %>% 
  slice(1)
country_information %>% 
  filter(country_worked_in_map == FALSE) %>% 
  group_by(country_worked) %>% 
  slice(1)
```

From that we see that the following countries are given as locations but not listed in the map data:
- United Kingdom of Great Britain and Northern Ireland  
- UK
- United States of America  
- Hong Kong (S.A.R.)  
  
The equivalent locations in the map data are:
- United Kingdom  
- United States  
- Hong Kong

Therefore need to change the names for plotting so that they align with the map data.

```{r aligning respondent countries with map data}
country_information <- country_information %>% 
  mutate(country_from = case_when(country_from == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
                                  country_from == "UK" ~ "United Kingdom",
                                  country_from == "United States of America" ~ "United States",
                                  country_from == "Hong Kong (S.A.R.)" ~ "Hong Kong",
                                         TRUE ~ country_from),
         country_worked = case_when(country_worked == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
                                    country_worked == "UK" ~ "United Kingdom",
                                    country_worked == "United States of America" ~ "United States",
                                    country_worked == "Hong Kong (S.A.R.)" ~ "Hong Kong",
                                         TRUE ~ country_worked)
  )
```

## Reshape and joing country information data to mapping

```{r create dataframe for demographic maps}
country_from_summarised <- country_information %>% 
  group_by(country_from) %>% 
  dplyr::summarise(from = n()) %>% 
  dplyr::rename(name_long = country_from)
country_worked_summarised <- country_information %>% 
  group_by(country_worked) %>% 
  dplyr::summarise(worked = n()) %>% 
  dplyr::rename(name_long = country_worked)
survey_data_summarised <- country_from_summarised %>% 
  left_join(country_worked_summarised)

world <- world %>% 
  left_join(survey_data_summarised)
```

## Making the plots

```{r making demographic maps}
plot_countries_from <- ggplot() +
  geom_sf(data = world,
          aes(fill = from,
              colour = from)
          ) +
  scale_fill_viridis_b(name = "", na.value="snow2", option = "C", end = 0.9) +
  scale_colour_viridis_b(name = "", na.value="snow3", option = "C", end = 0.9) +
  labs(title="Number of respondents from each country") +
  theme_minimal()

plot_countries_from
ggsave(here::here("figures", "R2_countries_from_map.png"),
  plot = plot_countries_from,
  device = "png",
  width = 183,
  units = "mm"
)


plot_countries_worked <- ggplot() +
  geom_sf(data = world,
          aes(fill = worked,
              colour = worked)
          ) +
  scale_fill_viridis_b(name = "", na.value="snow2", option = "C", end = 0.9) +
  scale_colour_viridis_b(name = "", na.value="snow3", option = "C", end = 0.9) +
  labs(title="Number of respondents working in each country") +
  theme_minimal()

plot_countries_worked

plot_both <- plot_grid(plot_countries_from, plot_countries_worked, ncol = 1)
plot_both

save_plot(here::here("figures", "R2survey_demographics_map.pdf"), plot_both, base_width = 183, base_height = 200, units = "mm")
```

# Polarisation analysis

need to make another version of tab, this time with the raw values rather than the percentages.

```{r}
polar <- r2_likert_responses %>% 
  filter(Name != "Lang",
         Name != "Country_from",
         Name != "Country_predominantely_work",
         Name != "Ocean_basin",
         Name != "Years_experience",
         Name != "Fishing_gear_exp",
         Name != "email",
         Name != "sector") %>% 
  mutate(q_number = Name) %>% 
  left_join(r2_likert_questions, by = "q_number") %>% 
  select(-Name, -q_number) %>% 
  pivot_longer(names_to = "name", values_to = "response", cols = 1:54) %>% 
  select(question, name, response) %>% 
  group_by(question, response) %>% 
  dplyr::summarise(count = n()) %>% 
  pivot_wider(names_from = response, values_from = count) %>% 
  select("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree",  "Strongly agree") %>% 
  replace_na(list("Strongly disagree" = 0,
                  "Somewhat disagree" = 0,
                  "Neither agree nor disagree" = 0,
                  "Somewhat agree" = 0,
                  "Strongly agree" = 0)) %>% 
               left_join(r2_likert_questions)
```

Now calculate the scores for each row/question
```{r}
agreement(as.vector(polar[1,2:6], mode = "numeric"))
agreement(as.vector(polar[2,2:6], mode = "numeric"))
agreement(as.vector(polar[3,2:6], mode = "numeric"))
agreement(as.vector(polar[4,2:6], mode = "numeric"))
agreement(as.vector(polar[5,2:6], mode = "numeric"))
agreement(as.vector(polar[6,2:6], mode = "numeric"))
agreement(as.vector(polar[7,2:6], mode = "numeric"))
agreement(as.vector(polar[8,2:6], mode = "numeric"))
agreement(as.vector(polar[9,2:6], mode = "numeric"))
agreement(as.vector(polar[10,2:6], mode = "numeric"))
agreement(as.vector(polar[11,2:6], mode = "numeric"))
agreement(as.vector(polar[12,2:6], mode = "numeric"))
agreement(as.vector(polar[13,2:6], mode = "numeric"))
agreement(as.vector(polar[14,2:6], mode = "numeric"))
agreement(as.vector(polar[15,2:6], mode = "numeric"))
agreement(as.vector(polar[16,2:6], mode = "numeric"))
agreement(as.vector(polar[17,2:6], mode = "numeric"))
agreement(as.vector(polar[18,2:6], mode = "numeric"))
agreement(as.vector(polar[19,2:6], mode = "numeric"))
agreement(as.vector(polar[20,2:6], mode = "numeric"))
agreement(as.vector(polar[21,2:6], mode = "numeric"))
agreement(as.vector(polar[22,2:6], mode = "numeric"))
agreement(as.vector(polar[23,2:6], mode = "numeric"))
agreement(as.vector(polar[24,2:6], mode = "numeric"))
agreement(as.vector(polar[25,2:6], mode = "numeric"))
agreement(as.vector(polar[26,2:6], mode = "numeric"))
agreement(as.vector(polar[27,2:6], mode = "numeric"))
agreement(as.vector(polar[28,2:6], mode = "numeric"))
agreement(as.vector(polar[29,2:6], mode = "numeric"))
agreement(as.vector(polar[30,2:6], mode = "numeric"))
agreement(as.vector(polar[31,2:6], mode = "numeric"))
agreement(as.vector(polar[32,2:6], mode = "numeric"))
agreement(as.vector(polar[33,2:6], mode = "numeric"))
agreement(as.vector(polar[34,2:6], mode = "numeric"))
agreement(as.vector(polar[35,2:6], mode = "numeric"))
agreement(as.vector(polar[36,2:6], mode = "numeric"))
agreement(as.vector(polar[37,2:6], mode = "numeric"))
agreement(as.vector(polar[38,2:6], mode = "numeric"))
agreement(as.vector(polar[39,2:6], mode = "numeric"))
agreement(as.vector(polar[40,2:6], mode = "numeric"))
agreement(as.vector(polar[41,2:6], mode = "numeric"))
agreement(as.vector(polar[42,2:6], mode = "numeric"))
agreement(as.vector(polar[43,2:6], mode = "numeric"))
agreement(as.vector(polar[44,2:6], mode = "numeric"))
agreement(as.vector(polar[45,2:6], mode = "numeric"))

p1 <- polarization(as.vector(polar[1,2:6], mode = "numeric"))
```

# IDENTIFYING QUESTIONS TO USE IN ROUND 3

```{r}
#How many questions would we ask again with a 70% threshold?
round3_questions_70 <- tab %>%
  filter(all_agree < 0.7) %>% 
  filter(all_disagree < 0.7)
nrow(round3_questions_70)
#Answer: 25

round3_questions_70 <- round3_questions_70 %>% 
  left_join(round3_question_key, by = c("question", "q_number")) %>% 
  mutate(question_with_number = paste(q_number_R3, question))  %>% 
  mutate(question_with_number = sub("_", ".", question_with_number)) %>% 
  mutate(question_with_number = factor(question_with_number, levels= c(
    "5.4 Only some practices that use 'legitimate' fishing\ngears can be adapted or mitigated to reduce their\nimpact to an appropriate level",
    "5.3 All practices that use 'legitimate' fishing gears\ncan be adapted or mitigated to reduce their impact\nto an appropriate level",
    "5.2 Poor or low capacity management - rather than\nspecific fishing practices - determines how\ndestructive a fishing activity is",
    "5.1 All fishing practices can be destructive (if not\ncarried out appropriately or maintained at an\nappropriate level)",
    "4.4 Shares some characteristics with the term\n'illegal, unreported and unregulated (IUU)\nfishing'",
    "4.3 Shares some characteristics with the term\n'overfishing'",
    "4.2 Is the same (conceptually) as the term 'fishing\nthat causes significant adverse impact'",
    "4.1 Is the same (conceptually) as the term 'illegal,\nunreported and unregulated (IUU) fishing'",
    "3.10 Fishing activity (or any other anthropogenic\nactivity) that infringes the legitimate rights of\nother fishers is destructive",
    "3.9 Proportional loss of a target species from fishing\nthat exceeds its biologically safe limits is\ndestructive",
    "3.8 Any mortality or injury to a non-target species\nfrom fishing (or any other anthropogenic activity)\nis destructive",
    "3.7 Any damage to a seabed habitat from fishing (or\nany other anthropogenic activity) is destructive",
    "3.6 Relates to the economic impact of financial loss\nto national economies",
    "3.5 Relates to the economic impact of financial loss\nto fishers/fishing enterprises",
    "3.4 Relates to the social impact of human rights\nviolation",
    "3.3 Relates to the social impact of conflict between\nsectors",
    "3.2 Relates to the social impact of traditional\nculture loss/degradation",
    "3.1 Relates to the social impact of traditional\nlivelihood loss/degradation",
    "2.7 Cannot be expressed universally (i.e. is always\ncontext-dependent)",
    "2.6 Describes changes/impacts that are avoidable",
    "2.5 Describes changes/impacts that are reversible over\nany time-scale",
    "2.4 Describes changes/impacts that are irreversible\nover any time scale",
    "2.3 Can describe an economic concept",
    "2.2 Can describe a social concept",
    "2.1 Has changed in its meaning over time"
)))

#What about a 75% threshold?
round3_questions_75 <- tab %>%
  filter(all_agree < 0.75) %>% 
  filter(all_disagree < 0.75)
nrow(round3_questions_75)
#Answer: 27
```

# MODIFIED FIGURE TO SHARE DURING ROUND 3

```{r}
highs_R3 <-tab3 %>% 
  ungroup() %>% 
  dplyr::filter(tab3$question %in% round3_questions_70$question) %>% 
  dplyr::filter(name == "Somewhat agree" |
                                 name == "Strongly agree" |
                                 name == "midhigh") %>% 
  left_join(round3_questions_70, by = "question") %>% 
  arrange(question_with_number)   %>% 
  mutate(question_with_number = factor(question_with_number, levels= c(
        "5.4 Only some practices that use 'legitimate' fishing\ngears can be adapted or mitigated to reduce their\nimpact to an appropriate level",
    "5.3 All practices that use 'legitimate' fishing gears\ncan be adapted or mitigated to reduce their impact\nto an appropriate level",
    "5.2 Poor or low capacity management - rather than\nspecific fishing practices - determines how\ndestructive a fishing activity is",
    "5.1 All fishing practices can be destructive (if not\ncarried out appropriately or maintained at an\nappropriate level)",
    "4.4 Shares some characteristics with the term\n'illegal, unreported and unregulated (IUU)\nfishing'",
    "4.3 Shares some characteristics with the term\n'overfishing'",
    "4.2 Is the same (conceptually) as the term 'fishing\nthat causes significant adverse impact'",
    "4.1 Is the same (conceptually) as the term 'illegal,\nunreported and unregulated (IUU) fishing'",
    "3.10 Fishing activity (or any other anthropogenic\nactivity) that infringes the legitimate rights of\nother fishers is destructive",
    "3.9 Proportional loss of a target species from fishing\nthat exceeds its biologically safe limits is\ndestructive",
    "3.8 Any mortality or injury to a non-target species\nfrom fishing (or any other anthropogenic activity)\nis destructive",
    "3.7 Any damage to a seabed habitat from fishing (or\nany other anthropogenic activity) is destructive",
    "3.6 Relates to the economic impact of financial loss\nto national economies",
    "3.5 Relates to the economic impact of financial loss\nto fishers/fishing enterprises",
    "3.4 Relates to the social impact of human rights\nviolation",
    "3.3 Relates to the social impact of conflict between\nsectors",
    "3.2 Relates to the social impact of traditional\nculture loss/degradation",
    "3.1 Relates to the social impact of traditional\nlivelihood loss/degradation",
    "2.7 Cannot be expressed universally (i.e. is always\ncontext-dependent)",
    "2.6 Describes changes/impacts that are avoidable",
    "2.5 Describes changes/impacts that are reversible over\nany time-scale",
    "2.4 Describes changes/impacts that are irreversible\nover any time scale",
    "2.3 Can describe an economic concept",
    "2.2 Can describe a social concept",
    "2.1 Has changed in its meaning over time"
)))

lows_R3 <- tab3 %>% 
  ungroup() %>%
  dplyr::filter(tab3$question %in% round3_questions_70$question) %>% 
  dplyr::filter(name == "Somewhat disagree" |
                                 name == "Strongly disagree" |
                                 name == "midlow") %>% 
  left_join(round3_questions_70, by = "question") %>% 
  arrange(question_with_number)   %>% 
  mutate(question_with_number = factor(question_with_number, levels= c(
        "5.4 Only some practices that use 'legitimate' fishing\ngears can be adapted or mitigated to reduce their\nimpact to an appropriate level",
    "5.3 All practices that use 'legitimate' fishing gears\ncan be adapted or mitigated to reduce their impact\nto an appropriate level",
    "5.2 Poor or low capacity management - rather than\nspecific fishing practices - determines how\ndestructive a fishing activity is",
    "5.1 All fishing practices can be destructive (if not\ncarried out appropriately or maintained at an\nappropriate level)",
    "4.4 Shares some characteristics with the term\n'illegal, unreported and unregulated (IUU)\nfishing'",
    "4.3 Shares some characteristics with the term\n'overfishing'",
    "4.2 Is the same (conceptually) as the term 'fishing\nthat causes significant adverse impact'",
    "4.1 Is the same (conceptually) as the term 'illegal,\nunreported and unregulated (IUU) fishing'",
    "3.10 Fishing activity (or any other anthropogenic\nactivity) that infringes the legitimate rights of\nother fishers is destructive",
    "3.9 Proportional loss of a target species from fishing\nthat exceeds its biologically safe limits is\ndestructive",
    "3.8 Any mortality or injury to a non-target species\nfrom fishing (or any other anthropogenic activity)\nis destructive",
    "3.7 Any damage to a seabed habitat from fishing (or\nany other anthropogenic activity) is destructive",
    "3.6 Relates to the economic impact of financial loss\nto national economies",
    "3.5 Relates to the economic impact of financial loss\nto fishers/fishing enterprises",
    "3.4 Relates to the social impact of human rights\nviolation",
    "3.3 Relates to the social impact of conflict between\nsectors",
    "3.2 Relates to the social impact of traditional\nculture loss/degradation",
    "3.1 Relates to the social impact of traditional\nlivelihood loss/degradation",
    "2.7 Cannot be expressed universally (i.e. is always\ncontext-dependent)",
    "2.6 Describes changes/impacts that are avoidable",
    "2.5 Describes changes/impacts that are reversible over\nany time-scale",
    "2.4 Describes changes/impacts that are irreversible\nover any time scale",
    "2.3 Can describe an economic concept",
    "2.2 Can describe a social concept",
    "2.1 Has changed in its meaning over time"
)))
```

Preparing the data for creating summary results to distribute in Round 3
```{r}
all_answers <-  r2_likert_responses %>%
  dplyr::rename(q_number = Name) %>% 
  right_join(round3_questions_70, by = "q_number")
```

# Figure of overall responses

```{r pressure, echo=FALSE}
Rd_3_likert_responses_fig <- ggplot() + geom_bar(data=highs_R3, aes(x = question_with_number, y=value, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows_R3, aes(x = question_with_number, y=-value, fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Response types", labels = mylevels, breaks=legend.pal, guide="legend") +
  theme_fivethirtyeight() + 
  coord_flip() +
  labs(y="Percentage of responses that agree or disagree with the statement",
       x="",
       title = "Questions from Round 2 without consensus",
       caption = "Figure shows all responses for the 25 statements that did not reach a threshold of 70% consensus, shown as a percentage\nof all responses. Positive values indicate agreement with the statement, negative values indicate disagreement.") +
  theme(plot.title = element_text(size=14, hjust=0.5)) +
  theme(axis.text.y = element_text(hjust=0)) +
  theme(legend.position = c(0.15, 0.93),
        legend.direction = "vertical") +
  scale_y_continuous(breaks=seq(mymin,mymax,25), limits=c(mymin,mymax))

Rd_3_likert_responses_fig

ggsave2(here::here("figures", "Rd_3_likert_responses_figure.pdf"),
  plot = Rd_3_likert_responses_fig,
  device = "pdf",
  width = 30,
  height = 35,
  units = "cm")
```

# Individual feedback figures
Now, create a loop or similar to create a figure for each individual. This section isn't run here because it generates individual figures, but retained here to show what was run to generate the indivdual feedback figures. 

```
#create list of names
respondents <- as.list(names(all_answers[,2:55]))
respondents <- sub(" ", "_", respondents)
names(all_answers) <- sub(" ", "_", names(all_answers))
all_respondent_figures <- list()
for( i in 1:length(respondents)) {
  respondent_name <- respondents[[i]]
  person <- all_answers %>% 
    select_if(colnames(.) %in% respondent_name | 
             colnames(.) == "question_with_number")
  colnames(person)[1] <- "person_name"
  person1 <- person$person_name
  names(person1) <- person$question_with_number
  
  individual_fig_Rd3 <- ggplot() + geom_bar(data=highs_R3, 
                                            aes(x = question_with_number, 
                                                y=value, fill=col),
                                            position="stack", stat="identity") +
  geom_bar(data=lows_R3, 
           aes(x = question_with_number, y=-value, 
               fill=factor(col, levels = c("#CA0020", "#F4A582", "#DFDFDF"))), 
           position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Response", 
                      labels = mylevels, breaks=legend.pal, guide="legend") +
  theme_fivethirtyeight() + 
  coord_flip() +
  labs(y="Question",
       x="",
       y.sec = "Your response",
       title = "Questions from Round 2 without consensus",
       subtitle = "                                                      Collated responses                                                 Your response",
       caption = "Figure shows all responses for the 25 statements that did not reach a threshold of 70% consensus, shown as a percentage of all responses. Positive values\nindicate agreement with the statement, negative values indicate disagreement. Your response to the statement is shown to the right of the figure.") +
  theme(plot.title = element_text(size=14, hjust=0.5)) +
  theme(axis.text.y = element_text(hjust=0)) +
  theme(legend.position = "bottom") +
  scale_y_continuous(breaks=seq(mymin,mymax,25), limits=c(mymin,mymax)) +
  guides(y.sec = guide_axis_manual(
    title = "Your response",
    breaks = names(person1),
    labels = person1))
  
  all_respondent_figures[[i]] <- individual_fig_Rd3
  individual_fig_name <- paste("Individual_fig_Rd3_", respondents[[i]], ".pdf", sep = "")
  
  ggsave2(here::here("Individual_figures_Rd_3", individual_fig_name),
  plot = individual_fig_Rd3,
  device = "pdf",
  width = 30,
  height = 35,
  units = "cm")
}
```

# Save the csv file of questions for using in Round 3
```{r}
write_csv2(round3_questions_70, file = here::here("data", "Round3_Questions.csv"), col_names = TRUE, escape = "double", quote = "all")
```